\documentclass[letterpaper,margin,line,11pt]{resume}
\usepackage[defblank]{paralist}
\usepackage{pdfpages}
\usepackage{anysize}
\usepackage[unicode]{hyperref}
\hypersetup{
    pdftitle={Michael Swan's Resume},
    pdfauthor={Michael Swan},
    pdfborder={0 0 0},
    unicode=true
}
\marginsize{0.5in}{1.8in}{0.5in}{0.5in}
\setdefaultitem{\footnotesize \textbullet}{}{}{}{}{}
\setdefaultleftmargin{0em}{}{}{}{}{}
\setdefaultenum{(a)}{(1)}{}{}{}{}
\newcommand{\rurl}[1]{\hfill {\footnotesize \url{#1}}}
\newcommand{\rdate}[1]{\hfill {\small #1}}
\renewcommand{\employer}[5]{\item[#1] - #2 \rdate{#3} \\* #4 \rurl{#5}}
\begin{document}
\name{\Large Michael Swan \hspace{92 mm} \footnotesize mswan@fastmail.com -- 610-428-4994}
\begin{resume}
\section{\mysidestyle Education}
    \begin{compactdesc}
        \item[University of Texas at San Antonio] - San Antonio, TX \rdate{Spring 2017 - Fall 2017}
        \small
        \\B.S. Computer Science
        \hfill 3.1 GPA
    \end{compactdesc}
    \begin{compactdesc}
        \item[Rochester Institute of Technology] - Rochester, NY \rdate{Fall 2012 - Spring 2016}
        \small
        \\Computer Science
    \end{compactdesc}

\section{\mysidestyle Experience}
    \begin{asparadesc}
        \employer{Raytheon}{San Antonio, TX} {August 2016 - Present}{\textit{Vulnerability Researcher \& Software Engineer}}{https://www.raytheon.com/}

        \small
	Analyzed various programs and consumer electronics for vulnerabilities, finding several that allow for remote
        code execution. Patched QEMU for reduced VM detection by guests. Added support for various Intel features to a
        hardware-accelerated state-of-the-art virtual machine. Wrote a small x86 bootloader program to unit test VM features.
        \normalsize
        \\

        \employer{Delphix}{San Francisco, CA} {June 2016 - August 2016}{\textit{Software Engineer Intern}}{https://www.delphix.com/}

        \small
        Made improvements to the Unix filesystem mounting abstractions used by the core Delphix product. Worked with a
        large team of programmers independently making changes to the same project.
        \normalsize
        \\

        \employer{Janssen Biotech}{Spring House, PA}{June 2015 - January 2016}{\textit{Software Engineer Intern}}{https://www.janssen.com/}

        \small
        Developed tooling and services for generating visualizations of tabular data sets, written predominantly in
        Haskell. Such datasets were often many gigabytes in size and so careful optimization was often necessary.
        \normalsize
        \\

        \employer{ShoreTel}{Rochester, NY}{June 2014 - December 2014}{\textit{Software Engineer Intern}}{https://www.shoretel.com/}

        \small
        Developed an HTTP load tester for slow internal services. Exposed particularly inefficent access patterns.
        \normalsize
    \end{asparadesc}

\section{\mysidestyle Languages}
    C, C++, Haskell, x86 Assembly, Erlang, Python, Coq, Verilog
    \hfill 
    \footnotesize 
    (In decreasing order of proficiency)
    \normalsize

\section{\mysidestyle Projects}
    \begin{compactdesc}
        \item[pcf-font] \rurl{https://github.com/michael-swan/pcf-font} \\
            Implemented a Haskell library for parsing and rendering X11 PCF fonts, which was later used for other
            projects involving text rendering with OpenGL and a font texture atlas.
        \item[Causal Commutative Arrow] \rurl{https://github.com/michael-swan/CausalCommutativeArrows} \\
            Wrote a mechanized proof in Coq of rewrite rules used for CCA optimization as described in the 2011 paper by
            Liu, Cheng, and Hudak.
        \item[Gameboy VGA Module] \rurl{https://github.com/michael-swan/Gameboy-RGB} \\
            Developed an FPGA device which converts video output from the classic Gameboy main board into a standard VGA
            output video signal.
        \item[NES Controller Serial-to-Parallel] \rurl{https://github.com/michael-swan/NES-Controller-SIPO} \\
            Created a module which converts serial data from NES controllers into a parallel bus for which separate
            wires correspond to separate buttons on the controller.
        \item[ProtectExec] \rurl{https://github.com/michael-swan/ProtectExec} \\
            Developed a simplified container system by configuring Linux control groups, namespaces, and chroot
            features in a simple C library.
        \item[Hardware Pong] \rurl{https://github.com/michael-swan/Pong} \\
            Implemented classic Pong on an FPGA with VGA output, written in Verilog.
        \item[SSH Honey Pot] \rurl{https://github.com/michael-swan/HoneyPot} \\
            Developed a simple SSH Honey Pot in Erlang.
    \end{compactdesc}

\end{resume}
\end{document}

